Cross-Validation Default

### 2023-07-03 minos/validation/cross_validation_S7.Rmd
Added equivalent_income to the list of vars that do inverse hyperbolic sine transformation when visualising with marginal plots

marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2016)

marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2018)

>>>>

marg_dist_densigram_plot_oneyear(observed = raw, 
                                 predicted = cv, 
                                 var = 'equivalent_income', 
                                 target.year = 2017)
